Analyzing Fairness: Race, Recidivism, and the COMPAS Algorithm

### 2022-04-17 final_metrics_analysis.Rmd
messing with processing

```{r py setup, include=FALSE}
library(reticulate)
```

@@

purple = '#9d0677'
green = '#30875c'
orange = '#E7881E'
blue = '#20A4CF'
workshop_palette = [purple, green]
df_viz.head()
```

@@

```{python exploratory race bar plot}
# barplot of race
sns.countplot(x="race", data=df_viz, palette=[blue, orange])
plt.title('Race Distribution (White and Black individuals only)')
```

```{python exploratory age by race plot}
# age distribution by race
ax = sns.kdeplot(x="age", hue="race", data=df_viz);
kdeline = ax.lines[0]
mean_fem = df_viz.groupby('race').age.median()[0]
xs = kdeline.get_xdata()
ys = kdeline.get_ydata()
height_fem = np.interp(mean_fem, xs, ys)
ax.vlines(mean_fem, 0, height_fem, color=blue, ls=':')

mean_m = df_viz.groupby('race').age.median()[1]
height_m = np.interp(mean_m, xs, ys)
ax.vlines(mean_m, 0, height_m, color=orange, ls=':')

print(df_viz.groupby('race').age.median())

plt.title('Distribution of Age by Race')
```

>>>>

```{r py setup, include=FALSE}
library(reticulate)

# for Dianne
use_condaenv("base")

# for Amrita
# use_condaenv("anaconda3")
```

@@

purple = '#9d0677'
green = '#30875c'
workshop_palette = [purple, green]
df_viz.head()
```

```{python average white and black defendant}
#av_defendant = (df_viz.groupby(['race'],as_index=False).age.mean()
```

@@

```{python exploratory race bar plot}
# barplot of race
sns.countplot(y="race", data=df_viz, palette=["#30875c"])
plt.title('Race Distribution (White and Black individuals only)')
```

```{python exploratory age by race plot}
# age distribution by race
#ax = sns.kdeplot(x="age", hue="race", data=df_viz);
#kdeline = ax.lines[0]
#mean_fem = df_viz.groupby('race').age.median()[0]
#xs = kdeline.get_xdata()
#ys = kdeline.get_ydata()
#height_fem = np.interp(mean_fem, xs, ys)
#ax.vlines(mean_fem, 0, height_fem, color=purple, ls=':')

#mean_m = df_viz.groupby('race').age.median()[1]
#height_m = np.interp(mean_m, xs, ys)
#ax.vlines(mean_m, 0, height_m, color=green, ls=':')

#print(df_viz.groupby('race').age.median())

#plt.title('Distribution of Age by Race')
```
